MSstatsPTM statistical relative quantification of post-translational modifications in global proteomics experiments\\ \textbf{Supplementary Information}

### 2022-08-12 main/MSstatsPTM_Main.tex
Results half-way through

We compared the performance of $MSstatsPTM$ to that of $Limma$ and $ANOVA$. Since $Isobar$-$PTM$ is only applicable to experiments with TMT labeling, it could not be applied to the datasets with known ground truth in this manuscript, and was excluded from the comparisons. All methods were compared both before and after adjusting for changes in the unmodified protein. $MSstatsPTM$ was compared to to base $MSstats$, modeled as seen in \eqref{msstats_model} on the peptide level. $ANOVA$ without adjustment was modeled as shown in \eqref{ttest_model}, and will be referred to as $basic$ $ANOVA$. $ANOVA$ with adjustment is referred to as $ANOVA$ and was modeled as in \eqref{ttest_ratio_model}. Finally, $Limma$ without adjustment uses the same model formula in \eqref{ttest_model}, while including a moderated variance estimation, and is referred to as $basic$ $Limma$. $Limma$ with adjustment is referred to as $Limma$ and was modeled as in \eqref{ttest_ratio_model} including moderated variance estimation. $MSstatsPTM$ was used without imputing missing values, and without Empirical Bayes moderation. All the evaluations were done at the FDR-adjusted p-value cutoff of $q=.05$. More details are in {\bf Supplementary Sec. \ref{supp-sec:experiments}}.

@@

\begin{equation}\label{eq:summary_stats}
\begin{alignedat}{2}
&\text{Accuracy} = \frac{TP + TN}{TP+TN+FP+FN}, \text{ Recall} = \frac{TP}{TP+FN} & \\
&1 - \text{PPV} = \frac{FP}{TP+FP} = \text{empirical False Discovery Rate (eFDR)}
\end{alignedat}
\end{equation}

For biological experiments with unknown ground truth, we compared the differentially abundant PTMs with and without adjusting for changes in unmodified protein abundance.

@@

\figref{sim1_fdr}(a) summarizes the eFDR reported on Computer Simulation 1 dataset by $MSstatsPTM$, $ANOVA$, $Limma$ and the basic $MSstats$, $ANOVA$ and $Limma$ methods. All the analyses were performed to control the eFDR at at most 5\%.  The  simulation mimics a ``clean" label-free experiment, not compromised by issues such as deviations from model assumptions, missing values and outliers. Yet, even under these favorable circumstances, the models that did not adjust for confounding from changes in overall protein abundance produced an excessive number of false positives. The versions of the models that accounted for the confounding produced error rates that were much better calibrated at the desired level. Since the simulation mimicked the assumptions of \todo{model XXX}, the error rates of this model were calibrated best.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection*{In noisy simulations, MSstatsPTM more accurately detected differentially modified modifications over the existing methods}

Figure \figref{sim2_acc} summarizes the results of the second computer simulation. The simulation is more realistic, and includes low modified feature counts and missing values. Differing numbers of conditions and replicates were compared in the presence of low and high noise. For low noise, $MSstatsPTM$ outperformed the existing methods across all conditions and number of replicates, with near 100\% accuracy when the replicates were high. As the noise increased the accuracy of all the methods decreased, however $MStatsPTM$ still outperformed the existing methods. The difference is primarily due to the robust nature of summarization in $MSstatsPTM$ through Tukey's Median Polish. The existing methods summation approach requires more observations to correctly summarize the intensities in the run, whereas TMP is robust to few measurements.

{\bf Supplementary Figure~\ref{supp-fig:fc_boxplot}} further compares the fold change estimation across all modified peptides. $MSstatsPTM$ showed a tighter distribution of estimated fold changes around the true fold change. Specifically, the inter-quartile range (IQR) of the estimated fold change for the proposed method was on average 32.5\% smaller than $Limma$ and $ANOVA$'s IQR. While the mean of the estimated fold changes was generally correct for all methods, the proposed approach correctly estimated the fold change more often across all PTMs.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection*{In the label-free benchmark experiment, MSstatsPTM had a higher sensitivity than the existing methods}

In this experiment all models incorrectly estimated the fold change of the modified spike-in peptides before adjusting for changes in unmodified protein abundance. After adjustment, the spike-in peptides' fold change was generally in line with expectation in all methods, however $MSstatsPTM$'s distribution of estimated fold changes was visibly tighter than the existing methods (\figref{spikein_boxplot}). Comparing the IQR of the spike-in peptide's log fold change, the proposed method's IQR was 32.86\% smaller than $Limma$ and $ANOVA$'s IQR. While $Limma$ and $ANOVA$ generally estimated the correct fold change, they were inconsistent in their estimation, resulting in a higher error rate. The proposed method's estimation was more consistent, with a smaller error. As discussed in the previous section, the summarization methods of the proposed methods excel when the number of observations are low. This was the case here, with each PTM only averaging $1.37$ features. The existing approaches used a non-robust summarization method, that was very sensitive to few observations, causing their fold change estimation to be more inconsistent, with a larger error compared to the proposed method.

In~\figref{spikein_prop_volcano} we can clearly see the fold change of the red labeled spike-in peptides was only correctly estimated when accounting for changes in the unmodified protein abundance. Additionally, the background peptides, serving as the null model, show many false positives before adjustment. After adjustment the number of false positives substantially decreased. Specifically, for the proposed method, the number of false positives went from 20.88\% to 1.84\% after adjustment was applied. While the proposed method and $Limma$ both correctly estimated the fold change of the spike-in peptides, using $Limma$ resulted in many large adjusted p-values. This was due to $Limma$ estimating a 35.7\% larger variance compared to the proposed method when estimating the spike-in peptides. This experiment introduced more variance components, which is challenging for the existing methods and therefore the difference in the results is more pronounced than in the simulations. Volcano plots for all methods and comparisons can be seen in {\bf Supplementary Section~\ref{supp-sec:benchmark}}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection*{In two group comparison TMT experiments, MSstatsPTM corrected for confounding with the unmodified protein}

The results of these experiments are summarized in~\figref{venn_diagrams} and~\figref{profile_plots}. \figref{venn_diagrams} shows the number of differentially abundant modified peptides before and after adjustment for Datasets 4 \& 5. Adjusting for changes in the unmodified protein caused more PTMs to change from differentially abundant to non-differentially abundant than vice versa. A question that must be addressed is if the decrease in differentially abundant peptides is due to the increased variance that comes from adjustment. This was tested by looking for modified peptides whose adjusted log fold change was within 10\% of the unadjusted log fold change but became statistically insignificant after adjustment. In other words, the fold change was the same between models but variance increased. When the test was applied to Dataset 4, only one PTM became non-differentially abundant due to an increase in variance. When applied to Dataset 5, 548 PTMs became non-differentially abundant due to an increase in variance (only 3.4\% of all PTMs that became non-differentially abundant). Thus we can conclude that the drop off in differentially abundant PTMs was due to changes in global protein abundance, not simply increased model variance.

@@

\begin{figure}[ht]
\centering
\includegraphics[scale=.55]{images/MSstatsPTM_design.png}
\caption{The $MSstatsPTM$ workflow. The names of the $MSstatsPTM$ R functions used for each step are highlighted in purple and the output notations are highlighted in red. The workflow begins with the acquisition of the enriched and global proteome lysates. The package is applicable to label-free data acquisitions such as DDA, DIA, SRM and label-based data acquisitions such as TMT. It takes as input lists of identified and quantified spectral features for the PTM and unmodified protein, produced by spectral processing tools such as MaxQuant, Progenesis, or Spectronaut.  Conversion, summarization and statistical modeling are performed separately for the PTM and for the unmodified proteins. Steps 4 and 5 leverage the summarization and modeling functions from $MSstats$ and $MSstatsTMT$. Model-based summaries are combined to adjust the changes in the PTM abundance for changes in unmodified protein abundance. Finally, sample size calculation for future experiments can be performed using the modeling output.}
\label{fig:msstatsptm_design}
\end{figure}

\begin{figure}[ht]
\centering
\begin{subfigure}[c]{0.7\linewidth}
\includegraphics[width=1\textwidth]{images/sim1_FDR_all_models.png}
\caption{}
\label{fig:sim1_fdr}
\end{subfigure}
\begin{subfigure}[c]{0.825\linewidth}
\includegraphics[width=1\textwidth]{images/sim3_Accuracy.png}
\caption{}
\label{fig:sim2_acc}
\end{subfigure}
\caption{Computer simulations. a) Dataset 1, clean simulation, analyzed to control eFDR at at most 5\% (horizontal line). The methods not accounting for the confounding between changes in PTM and overall changes in protein abundance produced exceedingly high numbers of false positives. In contrast, the methods accounting for the confounding correctly calibrated the proportion of false positive differentially abundant PTM.  b) In a noisy simulation, including limited feature observations and missing values, the advantage of the proposed approach was apparent. Looking at accuracy, the proposed method outperformed $ANOVA$ and $Limma$ in nearly every model.
}
\label{fig:computer_sim}
\end{figure}

\begin{figure}[ht]
\centering
\begin{subfigure}[c]{0.825\linewidth}
\includegraphics[width=1\textwidth]{images/spike_in_fc.png}
\caption{}
\label{fig:spikein_boxplot}
\end{subfigure}
\begin{subfigure}[c]{0.825\linewidth}
\includegraphics[width=1\textwidth]{images/spike_in_volcano.png}
\caption{}
\label{fig:spikein_prop_volcano}
\end{subfigure}
\caption{Dataset 3: Spike-in benchmark - Ubiquitination - Label-free. a) Before adjustment the fold change of the spike-in peptides' were systematically different from the expected fold change in all models. After adjustment, this systemic difference was removed, however the inner quartile range of the $Limma$ and $ANOVA$ models was wider than the proposed method. b) Before adjustment the spike-in peptides (colored red) did not follow the expected log fold change; after adjustment, the spike-in peptides were more in line with expectation. Using $Limma$, the spike-in peptides followed the expected log fold change after adjustment, however the majority of spike-in peptides did not have a significant adjusted p-value.}
\label{fig:spikein_volcano}
\end{figure}

>>>>

We compared the performance of $MSstatsPTM$ to that of $Limma$ and $ANOVA$, both before and after adjusting for changes in the unmodified protein. Since $Isobar$-$PTM$ is only applicable to experiments with TMT labeling, it could not be applied to the datasets with known ground truth in this manuscript, and was therefore excluded from the comparisons.

\todo{I am wondering if 'basic' is the right vocabulary here. Would you like to switch to 'unadjusted ANOVA', 'adjusted ANOVA', 'unadjusted Limma' and 'adjusted Limma', everywhere in the text and in the figures? }

$MSstatsPTM$ before adjusting for changes in the unmodified protein corresponds to base $MSstats$ or $MSstatsTMT$, modeled on the peptide level \todo{as described in Suppl Table XXX, as appropriate for the experimental design}. $MSstatsPTM$ with the adjustment, \todo{described in Sec XXX}, was used without imputing missing values, and without Empirical Bayes moderation.

$Basic$ $ANOVA$, i.e. $ANOVA$ before adjusting for changes in the unmodified protein, was as in \eqref{ttest_model}. $ANOVA$ with the adjustment was modeled as in \eqref{ttest_ratio_model}. 
Finally, $basic$ $Limma$ (i.e. without $Limma$ adjustment) used the same model formula in \eqref{ttest_model}, while including a moderated variance estimation. $Limma$ with adjustment was modeled as in \eqref{ttest_ratio_model} including moderated variance estimation.  
All the evaluations were done at the FDR-adjusted p-value cutoff of $q=.05$. More details are in {\bf Supplementary Sec. \ref{supp-sec:experiments}}.

@@

\begin{equation}\label{eq:summary_stats}
\begin{alignedat}{2}
&\text{Accuracy} = \frac{TP + TN}{TP+TN+FP+FN}, \text{ Recall} = \frac{TP}{TP+FN} & \\
&1 - \text{PPV} = \frac{FP}{TP+FP} = \text{empirical False Discovery Rate (eFDR)}
\end{alignedat}
\end{equation}
For biological experiments with unknown ground truth, we compared the differentially abundant PTMs with and without adjusting for changes in unmodified protein abundance.

@@

\figref{sim1_fdr} summarizes the eFDR reported on Computer Simulation 1 dataset by $MSstatsPTM$, $ANOVA$, $Limma$ and the basic $MSstats$, $ANOVA$ and $Limma$ methods. The  simulation mimicked a ``clean" label-free group comparison experiment, not compromised by issues such as deviations from model assumptions, missing values and outliers. All the analyses were performed to control the eFDR at at most 5\%.  Yet, even under these favorable circumstances, the models that did not adjust for confounding from changes in overall protein abundance produced an excessive number of false positives. The versions of the models that accounted for the confounding produced error rates that were much better calibrated at the desired level. \todo{Since the simulation mimicked the assumptions of model XXX?, the error rates of this model were calibrated best.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection*{In noisy simulations, MSstatsPTM more accurately detected differentially abundant PTM}

\figref{sim2_acc} summarizes the overall accuracy of methods adjusting for changes in the unmodified protein for Computer Simulation 2. The simulation mimicked a more realistic label-free group comparison experiment, including low counts of modified features and missing values. We evaluated the impact of low versus high noise, of the number of biological replicates, and of the number of conditions. For low noise, $MSstatsPTM$ outperformed the existing methods across all conditions and number of replicates, with near 100\% accuracy when the replicates were high. As the noise increased the accuracy of all the methods decreased, however $MStatsPTM$ still outperformed the existing methods. The difference is primarily due to the robust nature of summarization in $MSstatsPTM$ through Tukey's Median Polish.

{\bf Supplementary Figure~\ref{supp-fig:fc_boxplot}} further compares the fold change estimation across all modified peptides. $MSstatsPTM$ showed a tighter distribution of estimated fold changes around the true fold change. Specifically, the inter-quartile range (IQR) of the estimated fold change for $MSstatsPTM$ was on average 32.5\% smaller than $Limma$ and $ANOVA$'s IQR. While the mean of the estimated fold changes was generally correct for all the methods, the proposed approach correctly estimated the fold change more often across all PTMs.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection*{In the label-free benchmark experiment, MSstatsPTM had a higher sensitivity}

\figref{spikein_boxplot} summarizes the evaluation on the label-free spike-in group comparison experiment, for all the methods, with and without adjusting for changes in the unmodified protein. 
Without adjusting for changes in unmodified protein abundance, all the approaches incorrectly estimated the log$_2$-fold change of the modified spike-in peptides.
After adjustment, the estimation was generally in line with the ground truth for all methods, however $MSstatsPTM$'s distribution of estimated fold changes was tighter. 
\todo{On average over what?} the inter-quartile range of the estimates by $MSstatsPTM$ was 32.86\% smaller than that by $Limma$ or $ANOVA$. 
As seen in the previous section, the robust summarization by $MSstatsPTM$ was particularly useful when the number of \todo{features? Biological replicates?} was low. 
This was also the case in this experiment, with an average of $1.37$ features per PTM.

\figref{spikein_prop_volcano} details the detection of differentially abundant PTM for $MSstatsPTM$ and $Limma$, with and without the adjustment for changes in the unmodified protein.
As above, the log$_2$-fold changes of the spike-in peptides were only correctly estimated when accounting for changes in the unmodified protein abundance. 
Additionally, the background peptides, serving as the null model, show many false positives before adjustment. 
After adjustment the extent of false positives substantially decreased. 
Specifically, for $MSstatsPTM$ the number of false positives went from 20.88\% to 1.84\% after the adjustment. \todo{the numbers for Limma?} 
While the proposed method and $Limma$ both correctly estimated the fold change of the spike-in peptides, using $Limma$ resulted in many large adjusted p-values, and lower sensitivity. 
This experiment introduced more variance components \todo{not sure what you mean. The design is group comparison, and the model has only one variance component. Rephrase?}. 
On average \todo{over all the proteins in this experiment?}, the variance components estimates by $Limma$ were 35.7\% larger than for $MSstatsPTM$. Volcano plots for all methods and comparisons can be seen in {\bf Supplementary Section~\ref{supp-sec:benchmark}}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection*{In two biological experiments with TMT labeling, MSstatsPTM corrected for confounding with the unmodified protein}

The two results of these experiments are summarized in~\figref{venn_diagrams} and~\figref{profile_plots}. \figref{venn_diagrams} shows the number of differentially abundant modified peptides before and after adjustment for Datasets 4 \& 5. Adjusting for changes in the unmodified protein caused more PTMs to change from differentially abundant to non-differentially abundant than vice versa. A question that must be addressed is if the decrease in differentially abundant peptides is due to the increased variance that comes from adjustment. This was tested by looking for modified peptides whose adjusted log fold change was within 10\% of the unadjusted log fold change but became statistically insignificant after adjustment. In other words, the fold change was the same between models but variance increased. When the test was applied to Dataset 4, only one PTM became non-differentially abundant due to an increase in variance. When applied to Dataset 5, 548 PTMs became non-differentially abundant due to an increase in variance (only 3.4\% of all PTMs that became non-differentially abundant). Thus we can conclude that the drop off in differentially abundant PTMs was due to changes in global protein abundance, not simply increased model variance.

@@

\begin{figure}[ht]
\centering
\includegraphics[scale=.55]{images/MSstatsPTM_design.png}
\caption{The $MSstatsPTM$ workflow. \todo{in 6, maybe call it $J^{\prime}$ - in the figure and in the text?}The names of the $MSstatsPTM$ R functions used for each step are highlighted in purple \todo{distinguish bf and plain?} and the output notations are highlighted in red. The workflow begins with the acquisition of the enriched and global proteome lysates. The package is applicable to label-free data acquisitions such as DDA, DIA, SRM and label-based data acquisitions such as TMT. It takes as input lists of identified and quantified spectral features for the PTM and unmodified protein, produced by spectral processing tools such as MaxQuant, Progenesis, or Spectronaut.  Conversion, summarization and statistical modeling are performed separately for the PTM and for the unmodified proteins. Steps 4 and 5 leverage the summarization and modeling functions from $MSstats$ and $MSstatsTMT$. Model-based summaries are combined to adjust the changes in the PTM abundance for changes in unmodified protein abundance. Finally, sample size calculation for future experiments can be performed using the modeling output.}
\label{fig:msstatsptm_design}
\end{figure}

\begin{figure}[ht]
\centering
\begin{subfigure}[c]{0.7\linewidth}
\includegraphics[width=1\textwidth]{images/sim1_FDR_all_models.png}
\caption{}
\label{fig:sim1_fdr}
\end{subfigure}
\begin{subfigure}[c]{0.825\linewidth}
\includegraphics[width=1\textwidth]{images/sim3_Accuracy.png}
\caption{}
\label{fig:sim2_acc}
\end{subfigure}
\caption{Computer simulations. a) Dataset 1, clean simulation, analyzed to control eFDR at at most 5\% (horizontal line). The methods not accounting for the confounding between changes in PTM and overall changes in protein abundance produced exceedingly high numbers of false positives. In contrast, the methods accounting for the confounding correctly calibrated the proportion of false positive differentially abundant PTM.  b) In a noisy simulation, including limited feature observations and missing values, $MSstatsPTM$ had higher accuracy than $ANOVA$ and $Limma$ given the same noise, number of biological replicates, and number of conditions.
}
\label{fig:computer_sim}
\end{figure}

\begin{figure}[ht]
\centering
\begin{subfigure}[c]{0.825\linewidth}
\includegraphics[width=1\textwidth]{images/spike_in_fc.png}
\caption{}
\label{fig:spikein_boxplot}
\end{subfigure}
\begin{subfigure}[c]{0.825\linewidth}
\includegraphics[width=1\textwidth]{images/spike_in_volcano.png}
\caption{}
\label{fig:spikein_prop_volcano}
\end{subfigure}
\caption{Dataset 3: Spike-in benchmark - Ubiquitination - Label-free. \todo{explain the meaning of vertical solid vs dashed lines; and of the horizontal line} a) Before adjustment the fold change of the spike-in peptides' were systematically different from the expected fold change in all models. After adjustment, this systemic difference was removed, however the inner quartile range of the $Limma$ and $ANOVA$ models was wider than the proposed method. b) Before adjustment the spike-in peptides (colored red) did not follow the expected log fold change; after adjustment, the spike-in peptides were more in line with expectation. Using $Limma$, the spike-in peptides followed the expected log fold change after adjustment, however the majority of spike-in peptides did not have a significant adjusted p-value.}
\label{fig:spikein_volcano}
\end{figure}

### 2022-08-12 supplementary/ptm_sm.tex
Results half-way through

\title{MSstatsPTM statistical relative quantification of post-translational modifications in global proteomics experiments

\textbf{Supplementary Information}
}

@@

\begin{figure}[h!]
\makebox[\textwidth][c]{\includegraphics[width=1.2\textwidth]{sim_new/Statistical_inference}}%
\caption{Different models that are fit depending on the experimental design. Models are fit for Label-free and TMT acquisition methods, as well as group comparison and time course experimental designs. The estimation of standard error and degrees of freedom for each model is shown. \label{fig:statistical_inference}}
\end{figure}

@@

We compared six different approaches as follows: a) proposed approach, b) proposed approach without adjusting for unmodified peptides c) ANOVA~\cite{kutner_etal_04a} (with adjustment), d) ANOVA (no adjustment), e) Limma~\cite{Smyth:2004} (with adjustment), and f) Limma (no adjustment).

@@

\begin{figure}[h!]
\centering
 \begin{subfigure}{\textwidth}
 \centering
	\includegraphics[width=.8\textwidth]{sim_new/sim1_FC_boxplot}
	\caption{In simulation 1 all considered methods correctly estimated the fold change between conditions, with a median fold change estimation of 1. The distributions around the median were also consistent across all methods.}
 \end{subfigure}
 \begin{subfigure}{\textwidth}
  \centering
	\includegraphics[width=.8\textwidth]{sim_new/sim3_FC_boxplot}
	\caption{In simulation 2 all methods correctly estimated the fold change with a median log change of 1. The proposed method in this simulation had a visibly tighter distribution around the median. Both Limma and ANOVA showed a wider range around the fold change.}
 \end{subfigure}
\caption{Fold change distribution comparison between Simulations 1 and 2.}
\label{fig:fc_boxplot}
\end{figure}

>>>>

\title{MSstatsPTM statistical relative quantification of post-translational modifications in global proteomics experiments\\
\textbf{Supplementary Information}
}

@@

\begin{figure}[h!]
\makebox[\textwidth][c]{\includegraphics[width=1.2\textwidth]{sim_new/Statistical_inference}}%
\caption{Different models that are fit depending on the experimental design. Models are fit for label-free and TMT acquisition methods, as well as group comparison and time course experimental designs. The estimation of standard error and degrees of freedom for each model is shown. \label{fig:statistical_inference}}
\end{figure}

@@

\todo{Could you check that we have the same method names and fonts for the models here as in the main text?} We compared six different approaches as follows: a) proposed approach, b) proposed approach without adjusting for unmodified peptides c) ANOVA~\cite{kutner_etal_04a} (with adjustment), d) ANOVA (no adjustment), e) Limma~\cite{Smyth:2004} (with adjustment), and f) Limma (no adjustment).

@@

\begin{figure}[h!]
\centering
 \begin{subfigure}{\textwidth}
 \centering
	\includegraphics[width=.8\textwidth]{sim_new/sim1_FC_boxplot}
	\caption{\todo{not sure about the a and b labeling style. Could yo label the subfigures as (a) and (b), and combine the captions into a single caption, as in the main text?} In simulation 1 all considered methods correctly estimated the fold change between conditions, with a median fold change estimation of 1. The distributions around the median were also consistent across all methods.}
 \end{subfigure}
 \begin{subfigure}{\textwidth}
  \centering
	\includegraphics[width=.8\textwidth]{sim_new/sim3_FC_boxplot}
	\caption{In simulation 2 all methods correctly estimated the fold change with a median log change of 1. The proposed method in this simulation had a visibly tighter distribution around the median. Both Limma and ANOVA showed a wider range around the fold change.}
 \end{subfigure}
\caption{Fold change distribution comparison between Simulations 1 and 2.}
\label{fig:fc_boxplot}
\end{figure}
